Ford Fusion

### 2024-09-17 mss.tex
Push

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:2 (2024):  87–102. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Ford Fusion}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{87}

@@

Before Ford Fusion, each commit to the Clay filesystem validated its files using filetypes (called ``marks'') defined by files in the previous commit (see \citet{Davis2024}, pp. 33–48 in this issue). This could cause bugs if the filetype definitions had changed in a backward-incompatible manner. It also meant a commit could not add both a new filetype and new files of that type; instead, you needed two commits: one to define the filetypes, and a second to add files of that new type. More theoretically, it caused history-dependence. The validated contents of files in a commit could vary based on the history of commits that led to this one.

Another way source code failed to be self-contained was that it had access to symmetry-breaking information at build-time, namely ship, desk (Urbit's answer to a \textsc{git} branch), and (faked) date. A build recipe should be able to shared, cached, and rerun without dependence on local conditions, so user code now no longer learns its ship, desk, or date until runtime.

>>>>

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:2 (2024):  89–104. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Ford Fusion}
\fancyfoot[LE,RO]{\thepage}

@@

% We will adjust page numbering in final editing.
\pagenumbering{arabic}
\setcounter{page}{89}

@@

Before Ford Fusion, each commit to the Clay filesystem validated its files using filetypes (called ``marks'') defined by files in the previous commit (see \citet{Davis2024}, pp. 35–50 in this issue). This could cause bugs if the filetype definitions had changed in a backward-incompatible manner. It also meant a commit could not add both a new filetype and new files of that type; instead, you needed two commits: one to define the filetypes, and a second to add files of that new type. More theoretically, it caused history-dependence. The validated contents of files in a commit could vary based on the history of commits that led to this one.

Another way source code failed to be self-contained was that it had access to symmetry-breaking information at build-time, namely ship, desk (Urbit's answer to a \texttt{git} branch), and (faked) date. A build recipe should be able to shared, cached, and rerun without dependence on local conditions, so user code now no longer learns its ship, desk, or date until runtime.
